### 2016-09-28 Chapters/MathematicalResults.tex
Switch to Minion Pro

\section{The \texorpdfstring{$T_1$}{T1}-Transformation}\label{sec:T1-cc}

$T_1$ is a one-electron operator, carrying out a similarity transformation of
an operator $O$ by means of its exponential mapping will preserve the particle
rank of $O$.\autocite{Koch1994-vr}
Starting from the arbitrary order Lagrangian \eqref{eq:cc-lagrangian},
we want to derive their $T_1$-transformed
expressions.
For the \acrshort{CCS} model, this is straightforward.
The Lagrangian is:
\begin{equation}\label{eq:ccs-lagrangian}
 \mathcal{L}(\tamp{}, \tbar{})_\mathrm{CCS}
 =
  E_0
  + \tbar{\mu_1}\denom{\mu_1}\tamp{\mu_1}
  + \braket{\mathrm{HF} | \check{\Phi} | \mathrm{HF}}
  + \braket{\tbar{1} | \check{\Phi} | \mathrm{HF}}
\end{equation}
the governing equations:
\begin{subequations}\label{eq:ccs-equations}
  \begin{align}
   \denom{\mu_1}\tamp{\mu_1} &+ \braket{\mu_1 | \check{\Phi} | \mathrm{HF}}
             = 0 \label{eq:ccs-amplitudes}\\
    \denom{\mu_1}\tbar{\mu_1} &+
    \braket{\mathrm{HF} | \commutator{\check{\Phi}}{\cluster{\mu_1}} | \mathrm{HF}} +
    \braket{\tbar{1} |
    \commutator{\check{\Phi}}{\cluster{\mu_1}} | \mathrm{HF}}
             = 0 \label{eq:ccs-multipliers}
  \end{align}
\end{subequations}

@@

For the \acrshort{CCS} model, the expectation value of a one-electron operator
is simply:
\begin{equation}\label{eq:ccs-expectation-value}
\begin{aligned}
  O(\tamp{}, \tbar{})_\mathrm{CCS} &=
  \braket{\mathrm{HF} | \check{O} | \mathrm{HF} }
  + \braket{\tbar{1} | \check{O} | \mathrm{HF} } \\
  &=
  \braket{\mathrm{HF} | O + \commutator{O}{T_1} | \mathrm{HF} }
  + \braket{\tbar{1} | O + \commutator{O}{T_1}
  + \frac{1}{2}\commutator{\commutator{O}{T_1}}{T_1} | \mathrm{HF} }
\end{aligned}
\end{equation}
Adding double excitation to the manifold yields:
\begin{equation}\label{eq:ccsd-expectation-value}
  \begin{aligned}
  O(\tamp{}, \tbar{})_\mathrm{CCSD}
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCS}
  + \braket{\tbar{1} | \commutator{\check{O}}{T_2} | \mathrm{HF} }
  + \braket{\tbar{2} | \commutator{\check{O}}{T_2} | \mathrm{HF} } \\
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCS}
  + \braket{\tbar{1} | \commutator{O}{T_2} | \mathrm{HF} }
  + \braket{\tbar{2} | \commutator{O}{T_2}
      + \commutator{\commutator{O}{T_1}}{T_2}
  | \mathrm{HF} }
  \end{aligned}
\end{equation}
a number of terms was dropped thanks to Lemma \ref{lemma:exc-rank} and its
Corollary.
Eventually, including triples one obtains:
\begin{equation}\label{eq:ccsdt-expectation-value}
\begin{aligned}
  O(\tamp{}, \tbar{})_\mathrm{CCSDT}
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCSD}
  + \braket{\tbar{2} | \commutator{\check{O}}{T_3} | \mathrm{HF} } \\
  &+ \braket{\tbar{3} | \commutator{\check{O}}{T_3}
    + \frac{1}{2}\commutator{\commutator{\check{O}}{T_2}}{T_2}
  | \mathrm{HF} } \\
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCSD}
  + \braket{\tbar{2} | \commutator{O}{T_3} | \mathrm{HF} } \\
  &+ \braket{\tbar{3} | \commutator{O}{T_3}
    + \commutator{\commutator{O}{T_1}}{T_3}
    + \frac{1}{2}\commutator{\commutator{O}{T_2}}{T_2}
  | \mathrm{HF} }
\end{aligned}
\end{equation}
where Lemma \ref{lemma:exc-rank} and its corollary were again extensively employed.

The use of normal-ordered operators is common in \acrlong*{CC} theory. Both for
the dressed and bare representations, the expectation values of such operators
can be formed by simply replacing operator with its normal-ordered counterpart,
$\check{O}_\mathrm{N}$ or $O$, respectively.
This achieves elimination of the reference expectation value from the first
term in equation \eqref{eq:ccs-expectation-value}.

@@

In this Section, I will show how one can reformulate the transmission problem
in a variational fashion.
Such a formulation allows for a larger vector space, with weaker regularity
conditions, to be explored as solution space for the problem.
We will follow the exposition of \citeauthor{Ern2004-oo} quite closely
in introducing the \emph{weak} formulation of \glspl{PDE}.
For simplicity, we assume Dirichlet boundary conditions for a conductor,
\ie the basic assumption behind \acrshort{COSMO}.
The \emph{strong} formulation of the electrostatic problem then reads:
\begin{equation}\label{eq:poisson-cosmo}
  \nabla^2\esp = -4\pi\rho,
  \quad \esp \in \mathcal{C}^2_0(\Omegai),
\end{equation}
where $\mathcal{C}^2_0(\Omegai)$ is the vector space of twice
continuously differentiable functions in $\Omegai$ with null trace on
$\Gamma$.
We can relax this regularity requirement on $\Psi$ by introducing the
\emph{Hilbert Sobolev space} of test functions $H_0^1(\Omegai)$:
\begin{equation}
  H_0^1(\Omegai) = \lbrace
  f : \Omegai \rightarrow \mathbb{R}
  | f, \nabla f \in L^2(\Omegai), f_\Gamma = 0
  \rbrace.
\end{equation}
Projecting the differential problem onto this space and using the
$\eta\nabla^2\gamma = \nabla\cdot(\eta\nabla\gamma) - \nabla\eta\cdot\nabla\gamma$ identity
one obtains the \emph{weak} formulation of the differential problem:
\begin{equation}\label{eq:poisson-weak}
  \left\{
  \begin{aligned}
    &\text{Seek $\Psi \in H_0^1(\Omegai)$ such that:}\\
    &(\nabla\zeta, \nabla\Psi) =
    -4\pi(\zeta, \rho) \quad
    \forall \zeta\in H_0^1(\Omegai)
  \end{aligned}
  \right.
\end{equation}
The form $(\nabla\cdot, \nabla\cdot)$ is \emph{bilinear} and continuous
in $H_0^1(\Omegai)\times H_0^1(\Omegai)$, while $-4\pi(\cdot, \rho)$ is
\emph{linear} and continuous in $H_0^1(\Omegai)$.
We rewrite Eq. \eqref{eq:poisson-weak} in the abstract form:
\begin{equation}
  \left\{
  \begin{aligned}
    &\text{Seek $u \in V$ such that:}\\
    &\forall v \in V \,\,\,\,\,
    a(u, v) = b(v)
  \end{aligned}
  \right.
  \tag{\ref{eq:weak}}
\end{equation}
and state the following fundamental results:
\begin{lemma}[Lax--Milgram]
  If the bilinear form $a$ is \emph{continous} and \emph{coercive}
  in $V$, then, for any continuous linear form $b$, Problem~\eqref{eq:weak} is
  \emph{well-posed}.
\end{lemma}
\begin{corollary}[Variational property]
  If the bilinear form is \emph{symmetric} and \emph{positive}
  the unique solution to Problem \eqref{eq:weak} is
  the \emph{unique minimum} on $V$ of the functional:
  \[
  \mathcal{F}(u) = \frac{1}{2}a(u, u) - b(u)
  \]
\end{corollary}

>>>>

\section{The \texorpdfstring{$\T1$}{T1}-Transformation}\label{sec:T1-cc}

Carrying out a similarity transformation of
an operator $O$ by means of the $T_1$ cluster operator will preserve the particle
rank of $O$, since $T_1$ is a one-electron operator.\autocite{Koch1994-vr}
Starting from the arbitrary order Lagrangian \eqref{eq:cc-lagrangian},
we want to derive their $T_1$-transformed
expressions.
For the \acrshort{CCS} model, this is straightforward.
The Lagrangian is:
\begin{equation}\label{eq:ccs-lagrangian}
 \mathcal{L}(\tamp{}, \tbar{})_\mathrm{CCS}
 =
  E_0
  + \tbar{\mu_1}\denom{\mu_1}\tamp{\mu_1}
  + \braket{\mathrm{HF} | \check{\Phi} | \mathrm{HF}}
  + \braket{\tbar{1} | \check{\Phi} | \mathrm{HF}}
\end{equation}
the governing equations:
\begin{subequations}\label{eq:ccs-equations}
  \begin{align}
   \denom{\mu_1}\tamp{\mu_1} &+ \braket{\mu_1 | \check{\Phi} | \mathrm{HF}}
             = 0 \label{eq:ccs-amplitudes}\\
    \denom{\mu_1}\tbar{\mu_1} &+
    \braket{\mathrm{HF} | \commutator{\check{\Phi}}{\cluster{\mu_1}} | \mathrm{HF}} +
    \braket{\tbar{1} |
    \commutator{\check{\Phi}}{\cluster{\mu_1}} | \mathrm{HF}}
             = 0 \label{eq:ccs-multipliers}
  \end{align}
\end{subequations}

@@

For the \acrshort{CCS} model, the expectation value of a one-electron operator
is simply:
\begin{equation}\label{eq:ccs-expectation-value}
\begin{aligned}
  O(\tamp{}, \tbar{})_\mathrm{CCS} &=
  \braket{\mathrm{HF} | \check{O} | \mathrm{HF} }
  + \braket{\tbar{1} | \check{O} | \mathrm{HF} } \\
  &=
  \braket{\mathrm{HF} | O + \commutator{O}{T_1} | \mathrm{HF} }
  + \braket{\tbar{1} | O + \commutator{O}{T_1}
  + \frac{1}{2}\commutator{\commutator{O}{T_1}}{T_1} | \mathrm{HF} }
\end{aligned}
\end{equation}
Adding double excitations to the manifold yields:
\begin{equation}\label{eq:ccsd-expectation-value}
  \begin{aligned}
  O(\tamp{}, \tbar{})_\mathrm{CCSD}
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCS}
  + \braket{\tbar{1} | \commutator{\check{O}}{T_2} | \mathrm{HF} }
  + \braket{\tbar{2} | \commutator{\check{O}}{T_2} | \mathrm{HF} } \\
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCS}
  + \braket{\tbar{1} | \commutator{O}{T_2} | \mathrm{HF} }
  + \braket{\tbar{2} | \commutator{O}{T_2}
      + \commutator{\commutator{O}{T_1}}{T_2}
  | \mathrm{HF} },
  \end{aligned}
\end{equation}
where a number of terms was dropped thanks to Lemma \ref{lemma:exc-rank} and its
Corollary.
Eventually, including triples one obtains:
\begin{equation}\label{eq:ccsdt-expectation-value}
\begin{aligned}
  O(\tamp{}, \tbar{})_\mathrm{CCSDT}
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCSD}
  + \braket{\tbar{2} | \commutator{\check{O}}{T_3} | \mathrm{HF} } \\
  &+ \braket{\tbar{3} | \commutator{\check{O}}{T_3}
    + \frac{1}{2}\commutator{\commutator{\check{O}}{T_2}}{T_2}
  | \mathrm{HF} } \\
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCSD}
  + \braket{\tbar{2} | \commutator{O}{T_3} | \mathrm{HF} } \\
  &+ \braket{\tbar{3} | \commutator{O}{T_3}
    + \commutator{\commutator{O}{T_1}}{T_3}
    + \frac{1}{2}\commutator{\commutator{O}{T_2}}{T_2}
  | \mathrm{HF} }
\end{aligned}
\end{equation}
where Lemma \ref{lemma:exc-rank} and its corollary were again extensively employed.

The use of normal-ordered operators is common in \acrlong*{CC} theory. Both for
the dressed and bare representations, the expectation values of such operators
can be formed by simply replacing the operator with its normal-ordered counterpart,
$\check{O}_\mathrm{N}$ or $O$, respectively.
This achieves elimination of the reference expectation value from the first
term in equation \eqref{eq:ccs-expectation-value}.

@@

The transmission problem can be reformulated in a variational fashion.
Such a formulation allows for a larger vector space, with weaker regularity
conditions, to be explored as solution space for the problem.
We will follow the exposition of \citeauthor{Ern2004-oo} quite closely
in introducing the \emph{weak} formulation of \glspl{PDE}.
For simplicity, we assume Dirichlet boundary conditions for a conductor,
\ie the basic assumption behind \acrshort{COSMO}.
The \emph{strong} formulation of the electrostatic problem then reads:
\begin{equation}\label{eq:poisson-cosmo}
  \nabla^2\esp = -4\pi\rho,
  \quad \esp \in \mathcal{C}^2_0(\Omegai),
\end{equation}
where $\mathcal{C}^2_0(\Omegai)$ is the vector space of twice
continuously differentiable functions in $\Omegai$ with null trace on
$\Gamma$.
We can relax this regularity requirement on $\Psi$ by introducing the
\emph{Hilbert Sobolev space} of test functions $H_0^1(\Omegai)$:
\begin{equation}
  H_0^1(\Omegai) = \lbrace
  f : \Omegai \rightarrow \mathbb{R}
  | f, \nabla f \in L^2(\Omegai), f_\Gamma = 0
  \rbrace.
\end{equation}
Projecting the differential problem onto this space and using the
$\eta\nabla^2\gamma = \nabla\cdot(\eta\nabla\gamma) - \nabla\eta\cdot\nabla\gamma$ identity
one obtains the \emph{weak} formulation of the differential problem:
\begin{equation}\label{eq:poisson-weak}
  \left\{
  \begin{aligned}
    &\text{Seek $\Psi \in H_0^1(\Omegai)$ such that:}\\
    &(\nabla\zeta, \nabla\Psi) =
    -4\pi(\zeta, \rho) \quad
    \forall \zeta\in H_0^1(\Omegai)
  \end{aligned}
  \right.
\end{equation}
The form $(\nabla\cdot, \nabla\cdot)$ is \emph{bilinear} and continuous
in $H_0^1(\Omegai)\times H_0^1(\Omegai)$, while $-4\pi(\cdot, \rho)$ is
\emph{linear} and continuous in $H_0^1(\Omegai)$.
We rewrite Eq. \eqref{eq:poisson-weak} in the abstract form:
\begin{equation}
  \left\{
  \begin{aligned}
    &\text{Seek $u \in V$ such that:}\\
    &\forall v \in V \,\,\,\,\,
    a(u, v) = b(v)
  \end{aligned}
  \right.
  \tag{\ref{eq:weak}}
\end{equation}
and state the following fundamental results:
\begin{lemma}[Lax--Milgram]
  If the bilinear form $a$ is \emph{continous} and \emph{coercive}
  in $V$, then, for any continuous linear form $b$, Problem~\eqref{eq:weak} is
  \emph{well-posed}.
\end{lemma}
\begin{corollary}[Variational property]
  If the bilinear form is \emph{symmetric} and \emph{positive}
  the unique solution to Problem \eqref{eq:weak} is
  the \emph{unique minimum} on $V$ of the functional:
  \[
  \mathcal{F}(u) = \frac{1}{2}a(u, u) - b(u)
  \]
\end{corollary}

### 2016-09-28 FrontBackmatter/Colophon.tex
Switch to Minion Pro

\pdfbookmark[0]{Colophon}{colophon}
\section*{Colophon}
This document was typeset using \XeLaTeX, with the
\texttt{classicthesis} template developed by André Miede.\footnote{\url{https://bitbucket.org/amiede/classicthesis/}}
The style was inspired by Robert Bringhurst's seminal book on typography
\emph{The Elements of Typographic Style}.\autocite{Bringhurst2004-wn}
The bibliography was processed using
Biblatex\footnote{\url{https://www.ctan.org/pkg/biblatex}} and
Biber.\footnote{\url{http://biblatex-biber.sourceforge.net/}}
David J. Perry's Cardo provides both the text and display typeface.
Open Sans is the sans-serif typeface, while Bitstream Vera Mono is used
for monospaced text.
Finally, XITS acts at the math typeface.

\bigskip
{\small
\noindent\myTitle
\\
\noindent\textcopyright\,\finalVersion, \myName
}

>>>>

\pdfbookmark[1]{Colophon}{colophon}
\section*{Colophon}
This document was typeset using \XeLaTeX, with the
\texttt{classicthesis} template developed by André Miede.\footnote{\url{https://bitbucket.org/amiede/classicthesis/}}
The style was inspired by Robert Bringhurst's seminal book on typography
\emph{The Elements of Typographic Style}.\autocite{Bringhurst2004-wn}
The bibliography was processed using
Biblatex\footnote{\url{https://www.ctan.org/pkg/biblatex}} and
Biber.\footnote{\url{http://biblatex-biber.sourceforge.net/}}
Roberto Slimbach's Minion Pro provides both the text and display typeface.
\textsf{Open Sans} is the sans-serif typeface, while Jim Lyles's
\texttt{Bitstream Vera Mono} is used for monospaced text.
Finally, XITS acts at the math typeface.

\bigskip
{\small
\noindent\textit{\myTitle}
\\
\noindent\textcopyright\,\finalVersion, \myName
}
